Volunteers in the Clouds: an Architecture for Low Cost and Potentially Massive Distributed Evolutionary Computation

### 2015-08-07 volunteer-clouds-ieee-ci-si.tex
Homoneinizing JavaScript

Recent works propose the use of cloud computing services for the components of 
client-server distributed EAs. Cloud resources 
can reduce operational costs by outsourcing both hardware and software maintenance 
to the cloud provider. Another advantage is that they enable the provisioning of computing resources beyond what 
is available in most laboratories, allowing researches to 
scale algorithms at reasonable costs. Researchers have proposed the use of 
public clouds such as Amazon EC2 \cite{CloudScale}, Google App Engine\cite{di2013towards} 
and DropBox~\cite{mericloud}. The use of JavaScript to implement server side components, %FERGU: he puesto mejor el de revista en lugar del del CEC
gives software developers certain advantages in the cloud paradigm. JavaScript is a first-classe citizen
in most Platforms as a Service (PaaS) as many support the Node.js framework \cite{wood13:nodejs:paas}. Also many web services 
have native JavaScript libraries and use JSON for data interchange. Another advantage is that 
developers can use the same software tools for both client and server side development. 
Besides the advantages to deal with the same language in the full stack as previously mentioned, 
this also facilitates the interoperability of the exchanged data types.
%Ayuda con la mini conclusion FERGU: mira la última frase de arriba

@@

Javascript is also compatible with the functional programming paradigm \cite{Cousineau1998,MacLennan1990,Thompson1996}. 
According to \cite{swanresearch2015}, the benefits of using this kind of paradigm in 
metaheuristics optimization allows an improvement in communicability, 
reproducibility, interoperability, automated assembly, knowledge engineering 
and efficiency.

@@

%Si no se extiende mucho se podría también hablar de la conexión con Cloud Computing,
%se discuten las ventajas de utilizar Javascript para acceder a recursos donados por voluntarios
%pero falta hablar de como se explotaría el recurso Cloud. Lo digo por el titulo de Volunteers in the Clouds. Tal vez
%se deba hablar de la posibilidad de escalar los sistemas a bajo costo
%o según la demanda.

@@

Javascript has commonly been used to develop client-side scripts that handle the user interface,
communicate asynchronously with servers and update the content that is displayed \cite{flanagan2006javascript}.
Long-running scripts like those proposed in this work can interfere with the responsiveness of 
the web application, because everything is handled by a single thread. 
The Web Workers specification \cite{hickson2012web} defines an API that allows Web developers 
to execute long-running scripts in parallel with the scripts of the main page. 
Worker scripts are spawned in the background allowing a thread-like operation using 
message-passing as the communication mechanism between the worker's execution environment and the main thread. 
According to the Web Workers W3C Candidate Recomendation \cite{hickson2012web} 
workers are expected to be long-lived, they have a high start-up performance cost, 
and a high per-instance memory cost. The Web Worker API is implemented in current
versions of both desktop and mobile web browsers. For volunteer computing using the Web Worker API   
brings several advantages over a single threaded implementation:
\begin{itemize}
\item If the browser uses a tabbed document interface, the worker script 
keeps running in the background even it the user brings forward another tabbed window.
\item Several instances of the NodEO script can be executed in parallel in a single web page. 
\item Many immplemantations of the Web Worker API can use multiple CPUs for the execution
of worker scripts, in particular the execution in multiple CPUs was tested in desktop verions of
Chrome, FireFox and Safari.

>>>>

Recent works propose the use of cloud computing services for the components of 
client-server distributed EAs. Cloud resources 
can reduce operational costs by outsourcing both hardware and software maintenance 
to the cloud provider. Another advantage is that they enable the provisioning of computing resources beyond what 
is available in most laboratories, allowing researches to 
scale algorithms at reasonable costs. Researchers have proposed the use of 
public clouds such as Amazon EC2 \cite{CloudScale}, Google App Engine\cite{di2013towards} 
and DropBox~\cite{mericloud}. The use of JavaScript to implement
server side components, %FERGU: he puesto mejor el de revista en lugar
                        %del del CEC 
gives software developers certain advantages in the cloud
paradigm. JavaScript is a first-classe citizen 
in most Platforms as a Service (PaaS) as many support the Node.js
framework \cite{wood13:nodejs:paas}. Also many web services  
have native JavaScript libraries and use JSON for data
interchange. Another advantage is that  
developers can use the same software tools for both client and server
side development.  
Besides the advantages to deal with the same language in the full
stack as previously mentioned,  
this also facilitates the interoperability of the exchanged data types.
%Ayuda con la mini conclusion FERGU: mira la última frase de arriba

@@

JavaScript is also compatible with the functional programming paradigm \cite{Cousineau1998,MacLennan1990,Thompson1996}. 
According to \cite{swanresearch2015}, the benefits of using this kind of paradigm in 
metaheuristics optimization allows an improvement in communicability, 
reproducibility, interoperability, automated assembly, knowledge engineering 
and efficiency.

@@

%Si no se extiende mucho se podría también hablar de la conexión con Cloud Computing,
%se discuten las ventajas de utilizar JavaScript para acceder a recursos donados por voluntarios
%pero falta hablar de como se explotaría el recurso Cloud. Lo digo por el titulo de Volunteers in the Clouds. Tal vez
%se deba hablar de la posibilidad de escalar los sistemas a bajo costo
%o según la demanda.

@@

JavaScript has commonly been used to develop client-side scripts that handle the user interface,
communicate asynchronously with servers and update the content that is displayed \cite{flanagan2006javascript}.
Long-running scripts like those proposed in this work can interfere with the responsiveness of 
the web application, because everything is handled by a single thread. 
The Web Workers specification \cite{hickson2012web} defines an API that allows Web developers 
to execute long-running scripts in parallel with the scripts of the main page. 
Worker scripts are spawned in the background allowing a thread-like operation using 
message-passing as the communication mechanism between the worker's execution environment and the main thread. 
According to the Web Workers W3C Candidate Recomendation \cite{hickson2012web} 
workers are expected to be long-lived, they have a high start-up performance cost, 
and a high per-instance memory cost. The Web Worker API is implemented in current
versions of both desktop and mobile web browsers. For volunteer computing using the Web Worker API   
brings several advantages over a single threaded implementation:
\begin{itemize}
\item If the browser uses a tabbed document interface, the worker script 
keeps running in the background even it the user brings forward another tabbed window.
\item Several instances of the NodEO script can be executed in parallel in a single web page. 
\item Many immplemantations of the Web Worker API can use multiple CPUs for the execution
of worker scripts, in particular the execution in multiple CPUs was tested in desktop verions of
Chrome, FireFox and Safari.
